Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-04-18 manuscript.tex
new plotter for new measurement method (CAN)

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \dot{\rbM}\fe + \tfrac{1}{2}\fe^\top \ddtfrac{\rbM}{\fe}\fe
        \\
        =&
        \fe^\top (
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\rbu)
            -\rbd
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\rbu)-\rbu^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\overline\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.
\MSRY{여기서는 MVT, IFT을 사용하지 않았기 때문에 아이디얼 제어가 포화되지 않을 필요성이 없다. 실험에서도 포화를 핸들링하는 중에 추종이 완벽히 되지 못하는 것을 보인다.}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.99\linewidth]{src/figures/DNN.drawio.pdf}
    \caption{
        Architecture of the DNN $\NN({\q}_n;\wth)$ with $2$ hidden layers.
    }
    \label{fig:DNN}
\end{figure}

@@

In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and $\act^{*'}_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
Similarly, $\hat\NN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\hat \wth$, and define $\hat\act_i:=\act_i(\hat\NN_{i-1})$ and $\hat\act_i':= \pptfrac{\hat\act_i}{\hat\NN_{i-1}}$, respectively.

@@

The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\rbu}$ (\ie 
$
    \pptfrac{J}{\rbu}
    =
    ((\pptfrac{\fe}{\rbu})(\pptfrac{\rbu}{\estwth}))^\top \fe
    =
    ((\pptfrac{\fe}{\rbu})(\pptfrac{\estNN}{\estwth}))^\top \fe
$). 
Since the objective function depends on $\fe$ of a dynamic system, obtaining the gradient is not straightforward. 
The recommended method to calculate the exact value of $\pptfrac{J}{\estwth}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
\begin{equation}
    \ddtt (
        \pptfrac{\fe}{\rbu}
    )
    =
    \pptfrac{}{
        \rbu
    }
    \left[
        \rbM^{-1}(
            -\rbVm \fe
            -\mm K \fe
            + \mv f
            -\rbd + \mysat(\rbu)
        )
    \right]
    .
\end{equation}
However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\rbM,\rbVm, \rbF$ and $ \rbG$).
Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    (
        \Vert \estwth_i\Vert^2 
        -
        \overline\theta_i^2 
    )    
    \le 0
    \label{eq:cstr:weight:ball}
\end{equation}
with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j,
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight:ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight:ball:grad}, respectively.

@@

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes \hat\act_k^\top)}
        }_{:=c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\overline\tau+\overline\tau_d)
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

@@

Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
\begin{equation}
    \begin{aligned}
        \ddtt V_3
        =&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +\overline\tau_d\norm{\fe}
        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
        \\
        &
        -\estwth_k^\top (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        )
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +\fe^\top \estNN
        +(
            \overline\tau_d+\norm{
                \underbrace{
                    \idealNN+\mv\epsilon
                }_{=\rbu^*}
            }
        )
        \norm{\fe}
        \\
        &
        -\estNN^\top\fe 
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +(\overline\tau_d+\overline\tau)
        \norm{\fe}
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        .
    \end{aligned}
    \label{eq:lya3:dot}
\end{equation}
Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
\begin{equation}
    \Theta_{\fe}^{c_2}
    =
    \left\{ 
        \fe \in \R^n 
        \mid 
        \norm{\fe} 
        \le 
        \tfrac{
            \overline\tau_d+\overline\tau
        }{
            \lambda_{\min}(\mm K)
        }
    \right\}
    .
\end{equation}
The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.

@@

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
    %   \includegraphics
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % fig/Fig1.pdf
        src/script_simulation/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig11.eps
        src/script_simulation/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\tau$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights $\hat\theta_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/script_simulation/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

@@

% beta + zeta
For the cases of (C$_1$) and (C$_3$), the Lagrange multipliers $\lambda_{\rbu}$ adjusted the adaptation direction of the weights $\widehat{ \mv{\theta}}_1$ to reduce the constraint violation $c_{\rbu}$, as $\lambda_{\rbu}$ increased by the constraint violations.
% comparison; big, small beta
For more details, the effect of the update rate $\beta_j,\ \forall j\in\mathcal I$ of Lagrange multipliers is shown in Fig.~\ref{fig:lambda_effect} for convex constraint $c_j,\ \forall j\in\mathcal I$ and two different cases of $\lambda_j$.
With the bigger $\lambda_j$, the adaptation of $\widehat{ \mv{\theta}}_1$ is more assertive than that with smaller $\lambda_j$.
This leads to a faster satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, but this also causes oscillation in the adaptation process.
In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, $\lambda_j$ of (C$_1$) repeatedly increased and decreased, which indicates that the constraint $c_j,\ \forall j\in\mathcal I$ was satisfied and violated, respectively, in the discrete time implementation.
Besides, with small $\lambda_j$, the adaptation direction of $\widehat{ \mv{\theta}}_1$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_j$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
This allows the controller to show a smoother control input.
However, since the weights were adapted to reduce the filtered error $\fe$ while the control input was saturated, the weights were not able to effectively adapt the weights with respect to the filtered error $\fe$.

>>>>

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \rbM\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \rbM \ddtt \fe
        +
        \tfrac{1}{2}\fe^\top \dot{\rbM}\fe
        \\
        =&
        \fe^\top (
            -\rbVm \fe -\mm K \fe + \mv f
            -\rbd + \mysat(\rbu)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\rbM}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\rbu)
            -\rbd
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\rbM}- 2\rbVm)\fe
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\rbu))
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +
        \overline\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\rbu)-\rbu^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\rbu^*:= -\mv f$ is the ideal control input whose maximum norm is $\overline\tau$ according to Assumption \ref{assum:feasible} and $\mysat(\cdot)$. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\overline\tau_d}{\lambda_{\min}(\mm K)}$, if $\rbu=-\rbu^*$ can be realized.
However, $\rbu^*$ is not available in practice, since $\mv f$ is unknown.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.99\linewidth]{src/figures/DNN.drawio.pdf}
    \caption{
        Architecture of the DNN $\NN({\q}_n;\wth)$ with $k=2,l_0=2,l_1=l_2=3,l_3=2$.
    }
    \label{fig:DNN}
\end{figure}

@@

In the following sections, let $\idealNN_i$ represent the output of the $i\textsuperscript{th}$ layer with the ideal weight vector $\idealwth$. 
Additionally, define $\idealact_i:=\act_i(\idealNN_{i-1})$ and ${\idealact}'_i:= \pptfrac{\idealact_i}{\idealNN_{i-1}}$. 
Similarly, $\estNN_i$ denotes the output of the $i\textsuperscript{th}$ layer with the estimated weight vector $\estwth$, and define $\estact_i:=\act_i(\estNN_{i-1})$ and $\estact_i':= \pptfrac{\estact_i}{\estNN_{i-1}}$, respectively.

@@

The adaptation law for $\estwth$ defined in \eqref{eq:adap:th} involves the partial derivative of the state vector with respect to control input $\pptfrac{\fe}{\rbu}$ (\ie 
$
    \pptfrac{J}{\rbu}
    =
    \left(
        (\pptfrac{\fe}{\rbu})
        (\pptfrac{\rbu}{\estwth})
    \right)
    ^\top \fe
    =
    \left(
        (\pptfrac{\fe}{\rbu})
        (\pptfrac{\estNN}{\estwth})
    \right)
    ^\top \fe
$). 
Since the objective function depends on $\fe$ of a dynamic system, obtaining the gradient is not straightforward. 
The recommended method to calculate the exact value of $\pptfrac{J}{\estwth}$ is to use the forward sensitivity method \cite{Sengupta:2014aa} by simulating the sensitivity equation as follows: 
\begin{equation}
    \ddtt (
        \pptfrac{\fe}{\rbu}
    )
    =
    \pptfrac{}{
        \rbu
    }
    \left[
        \rbM^{-1}(
            -\rbVm \fe
            -\mm K \fe
            + \mv f
            -\rbd + \mysat(\rbu)
        )
    \right]
    .
\end{equation}
However, this method cannot be realized, since we do not have the exact system dynamics (\ie $\rbM,\rbVm, \rbF$ and $ \rbG$).
Additionally, the computational cost of the forward sensitivity method is high, as the number of NN's weights are generally large.

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in\{0,\cdots ,k\}}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    \left(
        \Vert \estwth_i\Vert^2 
        -
        \overline\theta_i^2 
    \right)    
    \le 0
    \label{eq:cstr:weight:ball}
\end{equation}
with $\overline\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j,
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight:ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight:ball:grad}, respectively.

@@

To investigate the boundedness of $\estwth_k$, consider the Lyapunov function candidate $V_2:=\tfrac{1}{2\alpha}\estwth_k^\top \estwth_k$.
Taking the time derivative of $V_2$ yields:
\begin{equation}
    \begin{aligned}
        \ddtt  V_2 
        =& 
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \textstyle\sum_{j\in\mathcal{I}}
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        =&
        -\estwth_k^\top 
        (
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        \\
        &
            +
            \textstyle\sum_{
                j\in\mathcal{I}\setminus \{\wth_i\}_{i\in[0,\cdots,k]}
            }
            \lambda_j 
            \pptfrac{c_j}{\estwth_k}
        )
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        \underbrace{
            \norm{(\mm I_{l_{k+1}}\otimes {\estact}_k^\top)}
        }_{:=c_1\in\R_{>0}}
        \norm{\fe}
        \norm{\estwth_k}
        \\
        &
        -
        \underbrace{
        \textstyle\sum_{
            j\in\mathcal{I}\setminus \{\wth_i\}_{i\in\{0,\cdots,k\}}
        }
        \lambda_j 
        \estwth_k^\top \pptfrac{c_j}{\estwth_k}
        }_{:= c_2 >0,\ \text{by Lemma \ref{lem:convex:angle} and Assumption \ref{assum:LICQ}}}
        \\
        \le&
        -
        \lambda_{\theta_k}\norm{\estwth_k}^2
        +
        c_1     
        \norm{\fe}
        \norm{\estwth_k}
        .
    \end{aligned}
    \label{eq:lya2:dot}
\end{equation}
According to \eqref{eq:lya2:dot}, the invariant set of $\estwth_k$ is defined as
\begin{equation}
    \Theta_{\theta_k}^{c_1} 
    = 
    \left\{ 
        \estwth_k \in \R^{\Xi_{k}} 
        \mid 
        \norm{\estwth_k} 
        \le 
        \tfrac{
            c_1(2\overline\tau+\overline\tau_d)
        }{
            \lambda_{\theta_k}\lambda_{\min}(\mm K)
        }
    \right\}
    .
    \label{eq:invariant:c1:wth}
\end{equation}

@@

Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
\begin{equation}
    \begin{aligned}
        \ddtt V_3
        =&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +\overline\tau_d\norm{\fe}
        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
        \\
        &
        -\estwth_k^\top (
            (\mm I_{l_{k+1}}\otimes \estact_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        )
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +\fe^\top \estNN
        +(
            \overline\tau_d+\norm{
                \underbrace{
                    \idealNN+\mv\epsilon
                }_{=\rbu^*}
            }
        )
        \norm{\fe}
        \\
        &
        -\estNN^\top\fe 
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        \\
        \le&
        -\lambda_{\min}(\mm K)\norm{\fe}^2
        +(\overline\tau_d+\overline\tau)
        \norm{\fe}
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        .
    \end{aligned}
    \label{eq:lya3:dot}
\end{equation}
Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
\begin{equation}
    \Theta_{\fe}^{c_2}
    =
    \left\{ 
        \fe \in \R^n 
        \mid 
        \norm{\fe} 
        \le 
        \tfrac{
            \overline\tau_d+\overline\tau
        }{
            \lambda_{\min}(\mm K)
        }
    \right\}
    .
\end{equation}
The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \overline\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.

@@

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
    %   \includegraphics
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % fig/Fig1.pdf
        src/script_simulation/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/script_simulation/figures/compare/Fig11.eps
        src/script_simulation/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\rbu$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/script_simulation/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights ${\estwth}_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/script_simulation/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

@@

% beta + zeta
For the cases of (C$_1$) and (C$_3$), the Lagrange multipliers $\lambda_{\rbu}$ adjusted the adaptation direction of the weights $\estwth_1$ to reduce the constraint violation $c_{\rbu}$, as $\lambda_{\rbu}$ increased by the constraint violations.
% comparison; big, small beta
For more details, the effect of the update rate $\beta_j,\ \forall j\in\mathcal I$ of Lagrange multipliers is shown in Fig.~\ref{fig:lambda_effect} for convex constraint $c_j,\ \forall j\in\mathcal I$ and two different cases of $\lambda_j$.
With the bigger $\lambda_j$, the adaptation of $\estwth_1$ is more assertive than that with smaller $\lambda_j$.
This leads to a faster satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, but this also causes oscillation in the adaptation process.
In Fig.~\ref{fig:ctrl:result:scope:control} and Fig.~\ref{fig:ctrl:result:scope:beta}, $\lambda_j$ of (C$_1$) repeatedly increased and decreased, which indicates that the constraint $c_j,\ \forall j\in\mathcal I$ was satisfied and violated, respectively, in the discrete time implementation.
Besides, with small $\lambda_j$, the adaptation direction of $\estwth_1$ is adjusted more conservatively, which leads to a slower satisfaction of the constraint $c_j,\ \forall j\in\mathcal I$, as shown in Fig.~\ref{fig:ctrl:result:scope:control} and the positively existence of $\lambda_j$ in Fig.~\ref{fig:ctrl:result:scope:beta}.
This allows the controller to show a smoother control input.
However, since the weights were adapted to reduce the filtered error $\fe$ while the control input was saturated, the weights were not able to effectively adapt the weights with respect to the filtered error $\fe$.
